\section{Relevant Experience}

\cventry{Oct 2025 – Apr 2026}{TAHO (early-stage startup)}%
{}%
{}%
{}%
{Product Engineer - Rust
\newline{• Deployed Qwen3-family models, optimizing memory and latency to enable practical local inference on commodity hardware.}
\newline{• Built graph visualization and debugging tooling used by engineers to inspect model execution and reason about decomposition strategies.}
\newline{• Integrated PyTorch, ONNX, and ORT to unify model conversion, execution, and validation workflows across heterogeneous systems.}
\newline{• Built and used LLM-assisted workflows (e.g., Claude Code) to accelerate debugging, code generation, and system exploration.}
\newline{• Identified limitations in Rust/ONNX tooling and translated them into concrete platform design constraints guiding system architecture.}
\newline{}
}

\cventry{Aug 2021 - May 2023}{Fuel Labs (early-stage startup)}%
{}%
{}%
{}%
{Compiler Engineer - Rust
\newline{• Contributed to the Sway smart contract language and compiler, used by a large developer ecosystem (61k+ \href{https://github.com/FuelLabs/sway}{{\color{navyblue}GitHub}} stars).}
\newline{• Implemented core language features (match expressions, traits, generics) informed by programming language research.}
\newline{• Translated developer feedback into language and tooling improvements, improving developer experience and usability.}
\newline{• Delivered talks and demos to onboard developers and improve adoption of language and tooling.}
\newline{}
}

\cventry{May 2021 – Aug 2021}{Google}%
{Madison, WI}%
{}%
{}%
{Software Engineering Intern - C++
\newline{• Implemented load balancing in a high-performance networking library using RMA-based RPC mechanisms.}
\newline{• Integrated low-level systems for efficient communication with network hardware.}
\newline{}
}

\cventry{June 2018 - May 2021}{Northeastern University, University of Massachusetts Amherst}%
{Boston, MA, Amherst, MA}%
{}%
{}%
{PhD Researcher - Rust, TypeScript, Python
\newline{• Built a serverless function accelerator compiling traced JavaScript into Rust to improve latency and throughput.}
\newline{• Led development across compiler, runtime, networking, and storage layers in a 0→1 system.}
\newline{• Implemented logging and debugging systems to diagnose non-deterministic behavior under limited observability.}
\newline{• Built and trained neural network models using TensorFlow/Keras with data preprocessing and evaluation pipelines.}
\newline{}
}

\cventry{June 2017 – Aug 2017}{National Aeronautics and Space Administration
(NASA)}%
{Langley, VA}%
{}%
{}%
{Software Engineering Intern - C++
\newline{• Contributed to GPS-based geofencing system for autonomous drones across heterogeneous platforms.}
\newline{• Tested and validated system behavior using simulated hardware environments.}
%\newline{}
}

%\cventry{June 2016 – Aug 2016}{General Electric (GE), Oil \& Gas}%
%{Billerica, MA}%
%{}%
%{}%
%{Information Technology Leadership Program (ITLP) Intern
%\newline{Created asset tracking system for shop floor using RFID, Bluetooth LE,
%and Raspberry Pi. Worked with the SAP enterprise resource management software to
%automate EHSM compliance checks.}%
%%\newline{}
%}