\section{Relevant Experience}

\cventry{Oct 2025 – Apr 2026}{TAHO (early-stage startup)}%
{}%
{}%
{}%
{Product Engineer - Rust
\newline{• Enabled large models (e.g., Qwen3, Stable Diffusion) to run on commodity hardware (e.g., Mac).}
\newline{• Built distributed AI inference infrastructure using streaming-first model decomposition.}
\newline{• Developed an IR enabling real-time graph decomposition without full model materialization.}
\newline{• Contributed to decomposition strategies including critical-node partitioning and planned operator/tensor-level extensions.}
\newline{• Designed low-latency execution under partial-information constraints.}
\newline{}
}

\cventry{Aug 2021 - May 2023}{Fuel Labs (early-stage startup)}%
{}%
{}%
{}%
{Compiler Engineer - Rust
\newline{• Built core components of the Sway smart contract language and compiler (61k+ \href{https://github.com/FuelLabs/sway}{{\color{navyblue}GitHub}} stars).}
\newline{• Contributed to the type system and type checker (trait resolution, name resolution, generic inference, diagnostics).}
\newline{• Improved compiler usability through language design (traits, match expressions, generics) and developer feedback.}
\newline{• Shaped AST design and mid-level compiler architecture across frontend, tooling, and backend teams.}
\newline{}
}

\cventry{May 2021 – Aug 2021}{Google}%
{Madison, WI}%
{}%
{}%
{Software Engineering Intern - C++
\newline{• Implemented load balancing in a high-performance networking library using RMA-based RPC mechanisms.}
\newline{• Integrated low-level systems for efficient communication with network hardware.}
\newline{}
}

\cventry{June 2018 - May 2021}{Northeastern University, University of Massachusetts Amherst}%
{Boston, MA, Amherst, MA}%
{}%
{}%
{PhD Researcher - Rust, TypeScript, Python
\newline{• Built a serverless function accelerator generating Rust from traced JavaScript executions, without requiring users to adopt Rust.}
\newline{• Enabled runtime switching from containerized execution to compiled Rust for improved latency and throughput.}
\newline{• Implemented a full-stack prototype spanning compiler, runtime, networking, and storage layers.}
\newline{}
}

\cventry{June 2017 – Aug 2017}{National Aeronautics and Space Administration
(NASA)}%
{Langley, VA}%
{}%
{}%
{Software Engineering Intern - C++
\newline{• Built GPS-based geofencing system for autonomous drones across heterogeneous platforms.}
\newline{• Tested and validated system behavior using simulated hardware environments.}
%\newline{}
}

%\cventry{June 2016 – Aug 2016}{General Electric (GE), Oil \& Gas}%
%{Billerica, MA}%
%{}%
%{}%
%{Information Technology Leadership Program (ITLP) Intern
%\newline{Created asset tracking system for shop floor using RFID, Bluetooth LE,
%and Raspberry Pi. Worked with the SAP enterprise resource management software to
%automate EHSM compliance checks.}%
%%\newline{}
%}