\section{Relevant Experience}

\cventry{Oct 2025 – Apr 2026}{TAHO (early-stage startup)}%
{}%
{}%
{}%
{Product Engineer - Rust
\newline{• Built developer tooling (graph visualization + TUI) to inspect and debug distributed model execution, enabling real-time introspection of partial graphs.}
\newline{• Designed an IR for streaming model decomposition, enabling developers to reason about execution without full model materialization.}
\newline{• Integrated PyTorch, ONNX, and onnxruntime to unify fragmented tooling and simplify debugging workflows across runtimes.}
\newline{• Investigated limitations in inference frameworks (especially ONNX in Rust) and translated findings into system design constraints and tooling improvements.}
\newline{• Deployed large-scale models (Qwen3) on commodity hardware under strict memory/latency constraints.}
\newline{}
}

\cventry{Aug 2021 - May 2023}{Fuel Labs (early-stage startup)}%
{}%
{}%
{}%
{Compiler Engineer - Rust
\newline{• Contributed to the Sway smart contract language and compiler, used by a large developer ecosystem (61k+ \href{https://github.com/FuelLabs/sway}{{\color{navyblue}GitHub}} stars).}
\newline{• Implemented core language features (match expressions, traits, generics) with a focus on developer ergonomics and usability.}
\newline{• Improved compiler diagnostics and error surfaces to reduce debugging friction for developers.}
\newline{• Translated developer feedback into language and tooling improvements across the compiler stack.}
\newline{• Delivered talks and demos to onboard developers and explain language and tooling design.}
\newline{}
}

\cventry{May 2021 – Aug 2021}{Google}%
{Madison, WI}%
{}%
{}%
{Software Engineering Intern - C++
\newline{• Implemented load balancing in a high-performance networking library using RMA-based RPC mechanisms.}
\newline{• Integrated low-level systems for efficient communication with network hardware.}
\newline{}
}

\cventry{June 2018 - May 2021}{Northeastern University, University of Massachusetts Amherst}%
{Boston, MA, Amherst, MA}%
{}%
{}%
{PhD Researcher - Rust, TypeScript, Python
\newline{• Built debugging and observability tooling for a serverless runtime with limited visibility.}
\newline{• Designed system enabling developers to transition from interpreted JS to compiled Rust without workflow disruption.}
\newline{• Developed full-stack prototype (compiler, runtime, networking) with focus on developer-facing abstractions.}
\newline{}
}

\cventry{June 2017 – Aug 2017}{National Aeronautics and Space Administration
(NASA)}%
{Langley, VA}%
{}%
{}%
{Software Engineering Intern - C++
\newline{• Contributed to GPS-based geofencing system for autonomous drones across heterogeneous platforms.}
\newline{• Tested and validated system behavior using simulated hardware environments.}
%\newline{}
}

%\cventry{June 2016 – Aug 2016}{General Electric (GE), Oil \& Gas}%
%{Billerica, MA}%
%{}%
%{}%
%{Information Technology Leadership Program (ITLP) Intern
%\newline{Created asset tracking system for shop floor using RFID, Bluetooth LE,
%and Raspberry Pi. Worked with the SAP enterprise resource management software to
%automate EHSM compliance checks.}%
%%\newline{}
%}