\section{Talks \& Panels}

\cvitem{}{
Blockchain Language Design panel.
\textit{Layer 2 Day at EthDenver.} 2023.
[\href{https://youtu.be/cH4BNwwZLv0?t=74}{{\color{navyblue}recording}}]
}

\cvitem{}{
Introduction to Fuel: Let's Get Modular talk.
\textit{Celestia's Modular Fellows.} 2022.
[\href{https://emilyaherbert.github.io/wiki/talks/2022/ModularFellows/}{{\color{navyblue}slides}}]
}

\cvitem{}{
Beyond Monolithic with Fuel: the Fastest Modular Execution Layer talk.
\textit{HackMoney.} 2022.
[\href{https://emilyaherbert.github.io/wiki/talks/2022/HackMoney/}{{\color{navyblue}slides}}]
}

\cvitem{}{
Scaling Execution: Optimistic panel.
\textit{The Modular Summit.} 2022.
}

\cvitem{}{
Developing Smart Contracts in Sway talk talk.
\textit{Layer2Amsterdam.} 2022.
[\href{https://emilyaherbert.github.io/wiki/talks/2022/Layer2Amsterdam/slides.pdf}{{\color{navyblue}slides}}]
}

\cvitem{}{
Sway: A Rust-based Smart Contract Language talk.
\textit{EthDenver.} 2022.
[\href{https://emilyaherbert.github.io/wiki/talks/2022/EthDenver/}{{\color{navyblue}slides}}]
}

\cvitem{}{
The Rollup Developer Experience panel.
\textit{EthDenver.} 2022.
[\href{https://www.youtube.com/watch?v=Tgk7eXUCgYk&t=1245s}{{\color{navyblue}recording}}]
}

\cvitem{}{
My Time From Trinity Until Now. \textit{Trinity University.} 2021.}

\cvitem{}{
A Language-based Serverless Function Accelerator talk.
\textit{Google PhD Intern Research Conference.} 2021.
}

\cvitem{}{
Graduate Student Life. \textit{Trinity University.} 2020.}

\cvitem{}{
A Language-based Serverless Function Accelerator talk.
\textit{Cornell CAPRA Lab.} 2020.
[\href{https://emilyaherbert.github.io/wiki/talks/2020/cornell-capra-lab.pdf}{{\color{navyblue}slides}}]
}

\cvitem{}{
NIM: Generative Neural Networks for Simulation Input Modeling talk.
\textit{SCS Summer Simulation Conference.} 2019.
[\href{https://emilyaherbert.github.io/wiki/talks/2019/summer-sim.pdf}{{\color{navyblue}slides}}]
}