\chapter {Simulation}

\section{Timeline}

\scalebox{1}{
\begin{tabular}{r |@{\foo} l}

2010 & Using Domain Specific Languages for Modeling and Simulation \cite{miller2010using} \\
2011 & Multi-agent System Simulation in Scala: An Evaluation of Actors for Parallel Simulation \cite{todd2011multi}

\end{tabular}
}

\section {Multi-agent System Simulation in Scala: An Evaluation of Actors for
Parallel Simulation \cite{todd2011multi}}
Proposes multi-agent simulation (MAS) in Scala that utilizes the Actor
framework. Satisfies motivations for removing possibility of race conditions.
Provides benchmarks comparing Actor framework to threads - Actor framework
displays slower results, but the prospect of safer simulations justifies the
slow-down.
\begin{itemize}
    \item \question{This design is outdated. What would a modern design look like?}
    \item \question{Would there be a motivation for simulation for RL agents?}
    \item Scala's delimited continuations library.
\end{itemize}

\section {Using Domain Specific Languages for Modeling and Simulation \cite{miller2010using}}
Gives an overview of the Scalation simulation DSL, implemented in Scala.
Discusses Scalation motivations and realizations, and how they make it a good
fit for Scala. Mentions use of Actors for parallel simulation, but does not
discuss further. System built on event graphs, ``where the nodes represent types
of events and the edges represent causal links between the events.''
\begin{itemize}
    \item \href{https://github.com/scalation/scalation}{https://github.com/scalation/scalation}
    \item Scala Parser Combinator Library.
    \item \question{What is the difference between a DSL and a library/ package?}
    \item Hyrid Functional Petri Nets.
    \item Fortress.
\end{itemize}